\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/sections/patterns_in_wrong_questions.tex
Update src/tex/sections/patterns_in_wrong_questions.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

The models seem to not be able to answer questions that require specific knowledge (e.g., safety profile of chemicals) and reasoning (e.g., oxidation number of a specific element, the number of chiral centers in an organic molecule or identifying a symmetry group).

\glspl{llm} also struggles with questions that require numerical outputs. Some of these involve multi-step calculations, which can be challenging for \glspl{llm}.\autocite{zhou2023llm_arithmetics}

>>>>

The models seem unable to answer questions that require specific knowledge (e.g., safety profile of chemicals) and reasoning (e.g., oxidation number of a specific element, the number of chiral centers in an organic molecule, or identifying a symmetry group).

\glspl{llm} also struggles with questions in \chembench that require numerical outputs. Some of these involve multi-step calculations, which can be challenging for \glspl{llm}.\autocite{zhou2023llm_arithmetics}
